MS797 Bigger Concepts

### 2022-02-25 _academics/ms797-bigger-concepts/ms797-bigger-concepts.Rmd
build

@@

The general umbrella categories for *classification*&mdash;where the outcome variable to be predicted is categorical, rather than continuous, like eye color rather than weight&mdash;are *discriminative" and "generative".

@@

The `foo.fit` summary will show the coefficients and p-values; the `$coef` aspect of the summary will show more detail.

>>>>

**This document is in process.**

@@

The general umbrella categories for *classification*&mdash;where the outcome variable to be predicted is categorical, rather than continuous, like eye color rather than weight&mdash;are "discriminative" and "generative". Discriminative models take sets of data and separate them into classes, like finding the decision boundary between two or more classes, but can't predict the values of new data. Generative models (used in unsupervised learning) can generate new data, but are more susceptible to outliers (misclassified observations) than discriminative models, require more data to create, and are more computationally expensive.

A generative model&mdash;somehow&mdash;tries to guess how the data was generated, so it can take a new bit of unseen data, assess the probability that each class would have produced it, and pick the class with the highest probability.

A discriminative model can only look at existing data and create a decision boundary separating the existing data into classes.

![Figure from https://stanford.edu/%7Eshervine/teaching/cs-229/cheatsheet-supervised-learning](disc-gen.png)

Note that there is no decision boundary in the generative model, just levels of probability into which new data could be classified with varying levels of confidence.

@@

The `zn.fit` summary above will show the coefficients and p-values; the `$coef` aspect of the summary will show more detail.
